Appendix

### 2020-03-04 manuscript/appendix.Rmd
describe grey diagonals in heatmap

```{r exploratory_heatmap, fig.cap = "Heatmap showing absolute value correlation coefficients among predictor variables.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```

>>>>

```{r exploratory_heatmap, fig.cap = "Heatmap showing Pearson correlation coefficients among predictor variables. Grey cells denote correlation matrix diagonals.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/08_exploratory_dotplot-1.pdf")
```
